%!TEX root = ../document.tex
\section*{Acknowledgements}
First and foremost we would like to thank our supervisor Anders Mørch. Your guidance and feedback throughout this thesis has been invaluable for us. We would like to thank Jo Herstad for inspiring chats and support and Hani Murad for help in structuring the work on this thesis. 

While working on this master thesis we have been located on the premise of Intermedia and Iped, thanks for letting us use the facilities at the institute, and the welcoming attitude in the hallways. Thanks to Alfredo Jornet Gil, Ingeborg Krange and Andres Kluge for valuable tips and suggestions.

A special thanks go to the students and the teacher in our design experiment. We would also like to thank the school and everybody who helped us make the data collection a reality.

Thanks to the students at the reading room at Iped, for helpful discussions and useful feedback. Thanks to Christopher and Christian for treasured ping pong matches.

We would also like to thank Sindre Eide, Estrid Hesselund, Tormod Smith Svanevik and Samuel Chattopadhyay-Reid for taking their time to read and provide useful feedback on this thesis.

Last but not least we would like to thank our family and friends for supporting us. And a special thanks to Lisa and Helena for love and support and for keeping up with a socio cultural perspective on everything.


% * Anders Mørch
% * Jo Herstad
% * Hani Murad
% * Erik Steineger
% * Elevene på Foss (dette må vel være anonymisert?)
% * Foss VGS
% * Hans Christian Rørkoll (han som initierte kontakt)
% * Intermedia
% * Iped
% * Studentene her
% * Alfredo, Ingeborg, Anders Kluge?
% * Sindre Eide, Estrid Hesselund
% * Tormod Smith Svanevik
% * Amerikaneren

\newpage